CPP_analysis

### 2019-10-24 CPP_analysis.Rmd
home

DI_summarize <- function(blockAB) {
DI_summary <- blockAB %>% 
  group_by(CageID) %>% 
  summarise(pop=first(Population), pp=mean(Photoperiod), lat=mean(Lat), block=first(Block), country=first(Country), h1=sum(H1Count), h2=sum(H2Count), emb=sum(EmbryoCount)) %>% 
  filter(h1+h2+emb>100)
DI_summary$total<-DI_summary$h1+DI_summary$h2+DI_summary$emb
DI_summary$DI<-DI_summary$emb/DI_summary$total
return(DI_summary)
}

@@

```{r collate_cpp_values}
cpp_2018<-data.frame(ED(d.model.fit, 50))
cpp_2018<-rownames_to_column(cpp_2018, var="pop") 
cpp_2018$pop<-str_sub(cpp_2018$pop,3,5)
popdata_2018<-DI_summary %>% group_by(pop) %>% 
  summarize(lat=first(lat), country=first(country))
cpp_2018<-right_join(cpp_2018, popdata_2018, by="pop")
cpp_2018$year<-rep("2018", nrow(cpp_2018))
colnames(cpp_2018)[colnames(cpp_2018)=="Std..Error"] <- "StdError"

@@

>>>>

DI_summarize <- function(blockAB) {
DI_summary <- blockAB %>% 
  group_by(CageID) %>% 
  summarise(pop=first(Population), pp=mean(Photoperiod), block=first(Block), lat=mean(Lat), block=first(Block), country=first(Country), h1=sum(H1Count), h2=sum(H2Count), emb=sum(EmbryoCount)) %>% 
  filter(h1+h2+emb>100)
DI_summary$total<-DI_summary$h1+DI_summary$h2+DI_summary$emb
DI_summary$DI<-DI_summary$emb/DI_summary$total
return(DI_summary)
}

@@

```{r collate_cpp_values}
cpp_2018<-data.frame(ED(d.model.fit, 50))
cpp_2018<-rownames_to_column(cpp_2018, var="pop") 
cpp_2018$pop<-str_sub(cpp_2018$pop,3,5)
popdata_2018<-DI_summary %>% group_by(pop) %>% 
  summarize(lat=first(lat), country=first(country), block=first(block))
cpp_2018<-right_join(cpp_2018, popdata_2018, by="pop")
cpp_2018$year<-rep("2018", nrow(cpp_2018))
colnames(cpp_2018)[colnames(cpp_2018)=="Std..Error"] <- "StdError"

@@

```{r}
ggplot(cpp_2018, aes(x=lat, y=Estimate, color=block)) + geom_point() + stat_smooth()
```
